Understanding GDP Relations to Crime in US Cities

### 2017-03-08 resource/index.Rmd
finished conclusion

>>>>

In conclusion we have found that in terms of actual *Crime Rate* population and GDP have very little affect on it and no affect in a statistically signifigant way.  And while there are trends that can be seen in the data when looking at the graphs it is still not to a great enought degree to consider those two variables as major drivers in the *Crime Rate*.  What is interesting is when we start to look at the differences between the many different values.  After running our models we have found that the change in the Population difference has a very pronounced affect on the crime difference.  So as the population difference increases the crime difference decreases.  The GPD difference though has an opposite affect on crime diffence.  As the GDP difference increases the crime difference decreases.  This seems to go against what can be thought of as common held beliefs.  The idead that when you live in a larger city there are more crimes, is true yet a person actual likelihood of committing a crime is decreased.  And where one would think that the better a cities economy is the less crime we foud the opposite.  All this points to is that there is much more to why crime happens then just the population and Gross Domestic Product.  While these two things can have an affect on it there is still much research that needs to be done in order to truly understand all of the nuances that go into this.

_If you want to look at our working code you can go to the repo [here](https://github.com/czross/info370-final)_
